Trustability of certification systems

### 2015-12-10 paper.tex
progress...

% Write abstract here
\begin{abstract}
This paper is a synthesis of a E.Gerck's paper : \textit{"Overview of Certification systems: X.509, CA, PGP and SKIP"}\cite{gerck1998overview}, but not only. It first gives an overview of (the mains) certification systems which are X.509 and CAs, PGP, SKIP, DANE and the Certificate transparency by Google, with a reflection on pros and cons of each system, on a technical point of view and about the government's stranglehold on data exchanges.
\end{abstract}

@@

\subsection{SKIP (Simple Key-Management for Internet Protocol)}

[...]

\subsection{X.509 and CAs}

@@

\subsection{PGP}

PGP\footnote{Pretty Good Privacy}, created thanks to Phil Zimmermann researches.

@@

\subsection{DANE}

DANE\footnote{DNS-Based Authentication of Named Entities} is not implemented yet, but a IETF team is working on the standard.

\subsection{Cetificate Transparency}

@@

>>>>

% Write abstract here
\begin{abstract}
This paper is a synthesis of a E.Gerck's paper : \textit{"Overview of Certification systems: X.509, CA, PGP and SKIP"}\cite{gerck1998overview}, but not only. It first gives an overview of (the mains) certification systems which are X.509 and CAs, PGP, SKIP, DANE and the Certificate transparency by Google, with thoughts on pros and cons of each system, on a technical point of view and about the government's stranglehold on data exchanges.
\end{abstract}

@@

First sections talk about existing (sections \ref{x509} and \ref{pgp}) or extinguished (section \ref{skip}) certification systems. Then, further sections (\ref{dane} and \ref{certtrans}) deals with new, not implemented yet, technologies of certification that may answer to current issues.

\subsection{X.509 and CAs}
\label{x509}

@@

\subsection{PGP (Pretty Good Privacy)}
\label{pgp}

PGP, created thanks to Phil Zimmermann researches.

@@

\subsection{SKIP (Simple Key-Management for Internet Protocol)}
\label{skip}

\subsection{DANE (DNS-Based Authentication of Named Entities)}
\label{dane}

DANE is not implemented yet, but a IETF team is working on the standard.

\subsection{Cetificate Transparency}
\label{certtrans}

@@

\bibitem{skip1995} Ashar Aziz, Tom Markson, Hemma Prafullchandra, Sun Microsystems, Inc., v.06, 1995. https://tools.ietf.org/html/draft-ietf-ipsec-skip-06
